Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-13 mtjournal.tex
Mari's notes on HTER comparison sections now included

Table~\ref{tab:hterpersent} presents per-sentence correlations,
weighted by sentence length.  Though many of the $r$ values are
smaller magnitude in this correlation, EDPM again has the largest
correlation in each category.  TER, however, does quite well with
length-weighted sentence correlation, with $r$ values within 95\%
confidence of EDPM scores on nearly every breakdown.

@@

TO DO: TERp optimizer [Matt, a brief description here]

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this featureset includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$
  decompositions.  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase table
  (4 features)  % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref)
\end{description}

@@

\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946  > 0.416
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827  > 0.404
      TB     0.3815  > 0.403
      ETNB   0.3814
      ETN    0.3804
      T      0.3758  > 0.398
      TNB    0.3708
      TN     0.3680  > 0.390
      TER    0.353   > 0.375
      E      0.3287  > 0.352
      EB     0.3267
      ENB    0.3149
      NB     0.3058  > 0.329
      EN     0.2973
      N      0.2636
      BLEU   0.244
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)

>>>>

%% MO: I still think this is a bit weird given that what you are
%% adding is structure. If time, you might want to look at some
%% example sentences
Table~\ref{tab:hterpersent} presents per-sentence correlations,
weighted by sentence length.  Though many of the $r$ values are
smaller magnitude in this correlation, EDPM again has the largest
correlation in each category.  TER, however, does quite well with
length-weighted sentence correlation, with $r$ values within 95\%
confidence of EDPM scores on nearly every breakdown.

@@

%% MO: important to describe basic model before listing features.
TO DO: TERp optimizer [Matt, a brief description here]

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this featureset includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$
  decompositions.  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % MO  (to Matt): is this basic TER or basic TERp?
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase table
  (4 features)  % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref).
  % MO: out of curiosity, why do you need 2 features?
  We assign two features here to let the system separately penalize
  ``too short'' translations and ``too long''.
\end{description}

@@

% MO suggestions:

%% do n-fold with >2 N -- better robustness to variation?

%% look at variation in weights on 2-fold case   
\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946  > 0.416
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827  > 0.404
      TB     0.3815  > 0.403
      ETNB   0.3814
      ETN    0.3804
      T      0.3758  > 0.398
      TNB    0.3708
      TN     0.3680  > 0.390
      TER    0.353   > 0.375
      E      0.3287  > 0.352
      EB     0.3267
      ENB    0.3149
      NB     0.3058  > 0.329
      EN     0.2973
      N      0.2636
      BLEU   0.244
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)
